---
title: "Ejercicio 1.7 guía speegle"
output: html_notebook
---

---

### Enunciado

R has a built-in vector rivers which contains the lengths of major North American rivers.

* Use ?rivers to learn about the data set.
* Find the mean and standard deviation of the rivers data using the base R functions mean and sd.
* Make a histogram (hist) of the rivers data.
* Get the five number summary (summary) of rivers data.
* Find the longest and shortest lengths of rivers in the set.
* Make a list of all (the lengths of the) rivers longer than 1000 miles.

---

Use ?rivers to learn about the data set.
```{r}
?rivers
```

Find the mean and standard deviation of the rivers data using the base R functions mean and sd.
```{r}
mean(rivers)
sd(rivers)
```

Make a histogram (hist) of the rivers data.
```{r}
hist(rivers)
```

Get the five number summary (summary) of rivers data.
```{r}
summary(rivers)
```

Find the longest and shortest lengths of rivers in the set.
```{r}
min(rivers)
max(rivers)
```

Make a list of all (the lengths of the) rivers longer than 1000 miles.
```{r}
rivers[rivers>1000]
```